Test Problems for Parallel Algorithms of Constrained Global Optimization

### 2017-10-05 2017/LION_Strongin/LION2017_BarkalovStrongin.tex
Unnecessary bracket has been deleted

The centers of the first two ''windows'', i.e. the pairs  $(t_1, q_1)$ and $(t_2, q_2)$, were chosen as the parameters for determining the specific problem statement. The values $q_1$ and $q_2$ were chosen independently and uniformly from the ranges  $[1,10]$ and $[-10, -1]$, respectively. The values $t_1$ and $t_2$ were dependent: first, the value $t_1$ was chosen from the range $[b+1, t_3-2]$, then, the value $t_2$ was chosen from the range $[t_1+1, t_3-1]$. All other parameters in problem (\ref{Eq:2}) were fixed: $a=1$, $b=10$, $t_3=18$, $q_0=q_3=0$, $\delta=0.3$. Parameter $\alpha$ from (\ref{Eq:8}) was chosen at $0.05$. The number of points in the additional grid $(\ref{Eq:6})$ for solving the least square problem (\ref{Eq:7}) was set at $20$. The problem of one-dimensional maximization and minimization from (\ref{Eq:9}) were solved by a scanning over a uniform grid of $100$ nodes within the interval $[a,b]$).

>>>>

The centers of the first two ''windows'', i.e. the pairs  $(t_1, q_1)$ and $(t_2, q_2)$, were chosen as the parameters for determining the specific problem statement. The values $q_1$ and $q_2$ were chosen independently and uniformly from the ranges  $[1,10]$ and $[-10, -1]$, respectively. The values $t_1$ and $t_2$ were dependent: first, the value $t_1$ was chosen from the range $[b+1, t_3-2]$, then, the value $t_2$ was chosen from the range $[t_1+1, t_3-1]$. All other parameters in problem (\ref{Eq:2}) were fixed: $a=1$, $b=10$, $t_3=18$, $q_0=q_3=0$, $\delta=0.3$. Parameter $\alpha$ from (\ref{Eq:8}) was chosen at $0.05$. The number of points in the additional grid $(\ref{Eq:6})$ for solving the least square problem (\ref{Eq:7}) was set at $20$. The problem of one-dimensional maximization and minimization from (\ref{Eq:9}) were solved by a scanning over a uniform grid of $100$ nodes within the interval $[a,b]$.
